Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
Credited Miguel Navascues and Denis Rosset in the acknowledgements section

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.} The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is simply not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.\footnote{This insight was originally made by Miguel Navascués in private communications.} Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes. In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes, one corresponding to $A, B$ correlations and another corresponding to $A, B$ anti-correlations.\footnote{This variation was originally suggested by Denis Rosset in private communications.} These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and should be a focus for future research.

    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_structure}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. Ultimately, it remains unclear whether or not a positive resolution to \ref{r:3} is even feasible.

    \begin{acknowledgments}
    This research was supported in part by Perimeter Institute for Theoretical Physics. Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science.
    \end{acknowledgments}

@@

    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}. Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal pre-injectable sets of $\graph'$, i.e. $\mscenario = \PreInj[\graph]{\graph'}$. This section acts as a reference for the particular inflations of the Triangle scenario that are mentioned throughout this manuscript. Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their pre-injectable sets. An efficient algorithm for computing the injectable and pre-injectable sets of an inflation can be found in~\cite{Inflation}.
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
    \caption{The Cut inflation.}\label{fig:cut_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}

>>>>

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.} The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is simply not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible. Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes. In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations. These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and should be a focus for future research.

    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_structure}) into the Triangle structure via the re-imagined version of the Triangle structure (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. Ultimately, it remains unclear whether or not a positive resolution to \ref{r:3} is even feasible.

    \begin{acknowledgments}
    This research was supported in part by Perimeter Institute for Theoretical Physics. Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science. The authors are grateful to Miguel Navascués for drawing our attention to the existence of distributions genuinely requiring quantum resources for all latent nodes in the Triangle structure. Moreover, the authors credit Denis Rosset for suggesting a Fritz distribution variant involving a reduced cardinality of outcomes.
    \end{acknowledgments}

@@

    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}. Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal pre-injectable sets of $\graph'$, i.e. $\mscenario = \PreInj[\graph]{\graph'}$. This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript. Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their pre-injectable sets. An efficient algorithm for computing the injectable and pre-injectable sets of an inflation can be found in~\cite{Inflation}.
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
    \caption{The Cut inflation.}\label{fig:cut_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
